Compositional equivalences based on Open pNets

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
corrected erroneous todos for tau transitions of holes
and added a summary table in last Appendix.

As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$. Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}

@@

\begin{example}
  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.  For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$. The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois. First rule \WTUn~ adds an $WT_\tau$ loop on each state. Rule \WTDeux~ transforms each 3 OTs into WOTs.   Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.   $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
         {\{\}, True,
			() }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+2) }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
  $\openrule
         {\emptyset, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
        {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).

@@

\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}

$WI_{12*}(n) = \openrule
{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
  {s \OTWeakarrow {\tau} s} 
s \in S$

@@

         And these numbers raise faster for other states, e.g. 13 WOTs for state 100.

>>>>

As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$. Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
%\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}

@@

\begin{example}
  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA. On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.  For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$. The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois. First rule \WTUn~ adds an $WT_\tau$ loop on each state. Rule \WTDeux~ transforms each 3 OTs into WOTs.   Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.   $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+1) }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
         {\{\}, True,
			() }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
         {\{\}, True,
			(\texttt{ec}\gets \texttt{ec}+2) }
         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
  $\openrule
         {\emptyset, True,
			(\texttt{ec}\gets \texttt{ec}+n) }
        {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).

@@

%\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
%
%$WI_{12*}(n) = \openrule
%{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
%  {s \OTWeakarrow {\tau} s} 
%s \in S$

\bigskip
The following table give a summary of  WOTs, when sharing their names as much as possible.

\begin{tabular}{|l|l|c|}
\hline
    WOT name & Pairs of source states and target states & \# of WOTs \\
    \hline
    $WI_1$ $WI_2$ $WI_\tau$ & $\{(s,s)| s \in \texttt{States of WOA}\} \cup \{(202,000)\} $ & 21 \\
    $WI_3(n)$ & \{(202,100),(000,100)\} & 2 \\
    $WI_{3a}(n)$ & \{(202,210),(000,210)\} & 2 \\
    $WI_{3b}(n)$ & \{(202,220),(000,220)\} & 2 \\
    $WI_{3c}(n)$ & \{(202,201),(000,201)\} & 2 \\
    $WI_4(n)$ $WI_4P(n)$ $WI_4Q(n)$ & \{(100,210)\} & 3 \\
    $WI_{4a}(n)$ $WI_4aP(n)$ $WI_4aQ(n)$ & \{(100,220)\} & 3 \\
    $WI_{456*}(n) $ $WI_{456*}P(n) $ $WI_{456*}Q(n) $ & \{(100,100)\} & 3 \\
    $WI_5(n)$ $WI_5P(n)$ $WI_5Q(n)$ & \{(210,220)\} & 3 \\
    $WI_{5a}(n)$ $WI_{5a}P(n)$ $WI_{5a}Q(n)$ & \{(210,100)\} & 3 \\
    $WI_{564*}(n) $ $WI_{564*}P(n) $ $WI_{564*}Q(n) $ & \{(210,210)\} & 3 \\
    $WI_6(n)$ $WI_6P(n)$ $WI_6Q(n)$ & \{(220,100)\} & 3 \\
    $WI_{6a}(n)$ $WI_{6a}P(n)$ $WI_{6a}Q(n)$ & \{(220,210)\} & 3 \\
    $WI_{645*}(n) $ $WI_{645*}P(n) $ $WI_{645*}Q(n) $ & \{(220,220)\} & 3 \\
    $WI_7(n)$ $WI_7P(n)$ $WI_7Q(n)$ & \{(210,201)\} & 3 \\
    $WI_{7a}(n)$ $WI_{7a}P(n)$ $WI_{7a}Q(n)$ & \{(220,201)\} & 3 \\
    $WI_{7b}(n)$ $WI_{7b}P(n)P$ $WI_{7b}Q(n)$ & \{(100,201)\} & 3 \\
    $WI_8(n)$ & \{(201,202),(201,000)\} & 2\\ 
    $WI_{8a}(n)$ & \{(210,202),(210,000)\} & 2 \\
    $WI_{8b}(n)$ & \{(220,202),(220,000)\} & 2 \\
    $WI_{8c}(n)$ & \{(100,202),(100,000)\} & 2 \\

    \hline
    \end{tabular}
    \bigskip
    That makes a total of 73 WOTs  in the SimpleImpl WOA.

@@

       Full list of WOTs
